Consistent Polyhedral Surrogates via Embedding

### 2019-05-15 notes/jessie-proof-sketches.tex
Separated out proofs into its own tex file

\documentclass[12pt]{article}
\PassOptionsToPackage{numbers, compress, sort}{natbib}
\usepackage{neurips_2019}

@@

\begin{abstract}
We formalize and study the natural approach of designing convex surrogate loss functions via embeddings for problems such as classification or ranking. 
In this approach, one embeds each of the finitely many predictions (e.g. classes) as a point in $\reals^d$, assigns the original loss values to these points, and convexifies the loss in between to obtain a surrogate.  
We prove that this approach is equivalent, in a strong sense, to working with polyhedral (piecewise linear convex) losses.  
Moreover, given any polyhedral loss $L$, we give a construction of a link function through which $L$ is a consistent surrogate for the loss it embeds.  
We illustrate the power of this embedding framework with succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature.
\end{abstract}

%  Convex surrogates are sweet.
%  Given a loss for a classification-like problem, there are two natural approaches to design convex surrogates.
%  First, one may attempt to map each prediction to a low-dimensional vector, and try to find a convex loss in that space with the right calibration.
%  Second, one may simply try to find a surrogate within the class of piecewise-linear convex, or polyhedral, losses.
%  We show an equivalence between these two approaches, and \raf{more stuff}.
%  We show that every loss with a finite number of predictions has a convex surrogate in the above sense using one fewer dimension that the number of outcomes, and give a full characterization of the losses needing only $d$ dimensions for such a surrogate.
%  We then apply this characterization to show novel lower bounds for abstain loss, demonstrating the power of our techniques over \raf{check this} alternatives such as feasible subspace dimension.

%\begin{keywords}%
%  information elicitation, proper scoring rules, surrogate loss functions
%\end{keywords}

@@

%\raf{MOVED FROM SEC 2; maybe incorporate?}
%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
%We now formalize this procedure.
%

Convex surrogate losses are a central building block in machine learning for classification and classification-like problems.
A growing body of work seeks to design and analyze convex surrogates for given loss functions, and more broadly, understand when such surrogates can and cannot be found.
For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space~\cite{frongillo2015elicitation,  ramaswamy2016convex}.
Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\cite{bartlett2008classification, yuan2010classification, ramaswamy2016convex, ramaswamy2018consistent}.
Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well-understood.

We augment this literature by studying a particularly natural approach for finding convex surrogates, wherein one ``embeds'' a discrete loss.
Specifically, we say a convex surrogate $L$ embeds a discrete loss $\ell$ if there is an injective embedding from the discrete reports (predictions) to a vector space such that (i) the original loss values are recovered, and (ii) a report is $\ell$-optimal if and only if the embedded report is $L$-optimal.
If additionally there exists a ``separated'' link function which maps approximately $L$-optimal reports to $\ell$-optimal reports, this condition is known to produce $\ell$-calibrated surrogates~\cite{agarwal2015consistent}.
Common examples which follow this general construction include hinge loss as a surrogate for 0-1 loss and the abstain surrogate mentioned above.

Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (piecewise-linear convex) loss functions.
In particular, by focusing on Bayes risks, we show that every discrete loss is embedded by some polyhedral loss, and every polyhedral loss function embeds some discrete loss.
Moreover, we show that any polyhedral loss gives rise to a separated link function to the loss it embeds, \raft{TODO: prove this :-]}
thus giving a very general framework to construct calibrated convex surrogates for arbitrary losses.

We go on to initiate a study of \emph{embedding dimension}: the minimal dimension for a given discrete loss to be so embedded.
Our results give a complete characterization in the case of dimension 1; that is, real-valued surrogates.
We find that a discrete loss can be embedded in the real line if and only if it is order-sensitive, meaning there is an ordering of the predictions such that the loss increases as one moves away from the correct prediction.
We show further that order-sensitivity characterizes the existence of \emph{any} real-valued convex surrogate, implying that embeddings lose no generality.
We conclude with preliminary results in higher dimensions and other future directions.

\subsection{Related works}
Convex surrogates have been formalized and investigated in a variety of past work such as \cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification}, particularly in the context of 0-1 loss, distributions on just two outcomes, and support vector machines.
%  \cite{crammer2001algorithmic} is one of the first papers to present a convex surrogate for multiclass classification problems in the context of support vector machines.
%  They use the convex surrogate $L(\textbf{r},y) = (\max_{j\neq y} r_j - r_y + 1)_+$, where $\textbf{r}$ is a $n$-dimensional vector corresponding to the entire distribution, and $r_j$ is the $j^{th}$ component of \textbf{r}.
%
%  \cite{bartlett2006convexity} provides one of the most well-known formalizations of convex surrogates for properties on binary outcomes.
%  This work evaluates the risk bounds of convex surrogates and shows the sufficiency of convex surrogates such as logistic loss to replace the 0-1 loss for ease of optimization, and has inspired a line of research in the design of consistent surrogate losses for binary classification problems.
%  \jessiet{This is based on what I remember.  Couldn't find the free version (off the campus network) but also didn't look hard at all, since I'm guessing one of you two already knows this paper better than I do.}
%
%%  \cite{bartlett2008classification} studies the abstain property with $n=2$ and shows a variation of the hinge loss that is one convex surrogate that elicits the abstain property to two outcomes.
%
%  \cite{ramaswamy2012classification} discuss and formalize the notion of \emph{convex calibration} dimension for finite properties.
%  The concept they call convex calibration dimension is one notion of elicitation complexity discussion in this paper.
%  Denoted here by $\eliccvx(\gamma)$, convex calibration refers to the minimum dimension $d$ such that the property $\gamma$ can be indirectly elicited by a convex loss $L:\reals^d \to \reals^\Y_+$.
%
%  Most of the preliminary work on the construction of convex surrogate losses focuses on learning the mode in a binary classification problem.
  One of the first works formally studying convex surrogates beyond binary outcomes is~\cite{ramaswamy2018consistent}, who give an embedding of the \emph{abstain loss} into very few dimensions.
For the case of $\reals^2$ \jessiet{$\reals^2$ or $n \in \{3, 4\}$?}, we will show that no embedding can do better.
%  Rather than focusing on the mode, this paper proves bounds on the elicitation complexity of the abstain property.
%  They provide a consistent surrogate that elicits abstain with $\alpha = 1/2$ in $\ceil*{\log_2 n}$ dimensions. \jessiet{I don't like how much I'm talking about elicitation without the context.}
%  It remains unknown if this bound is tight, although in Conjecture~\ref{conj:abstain-tight}, we conjecture that it is, at least from the perspective from ``embedding''.
%  If true, then we will need new approaches in order to indirectly elicit the abstain property by a convex surrogate for any dimension lower than $\ceil*{\log_2 n}$.
%
%  \cite{agarwal2015consistent} introduces the notion of a \emph{calibrated property}, which is very similar to our \emph{surrogate property} that we elicit by a convex surrogate in lieu of directly eliciting a finite property.
%  However, they do not consider properties to be set-valued, leading to subtle differences in the property values for some distributions.
%  Additionally, most of their results focus on linear properties. \jessiet{is there a relationship between linear and orderable properties?  If not, we can probably remove this statement.}
%
  \citet{agarwal2015consistent} and~\citet{ramaswamy2016convex} study the existence of convex surrogates; the latter proves lower bounds on dimensionality of hypothesis spaces for e.g.~0-1 loss via their notion of feasible subspace dimension.
  These works are generally not directly comparable to our results, as they do not consider the embedding method. \jessiet{In what sense do they not consider embedding?  The formalism we present?  They intuitively embed into the reals, but I don't remember if they focus on polyhedral losses}
  However, we will mention relevant results inline.
%  In~\cite{ramaswamy2016convex}, the authors introduce a new method of obtaining upper bounds on elicitation complexity called the \emph{Feasible Subspace Dimension}.
%  This method uses local information about distributions in a property in order to find bounds on the convex elicitation complexity of a property.
%  For example, Feasible Subspace Dimension can be used to find a tight bound on $\eliccvx$(mode), but does not reveal a tight bound for the abstain property discussed later.
%  This suggests that the bound on $\eliccvx$(abstain) must be found using more \emph{global} information about the property.
%  We discuss this in Section~\ref{sec:general-dimensions}, showing previously unknown necessary conditions for embedding finite properties.

% \subsection{Notation}
% \begin{itemize}
%   \item $\Y$ is the finite outcome space, and $n := |\Y|$.
%   \item $\simplex\subseteq\reals^\Y$ is the set of distributions over $\Y$, thought of as vectors of probabilities.
%   \item For an outcome $y$, we denote $p_y$ as the probability of outcome $y$ being observed in nature.
%   \item If $\gamma = \prop{\ell}$, then $\gamma:\simplex \toto \R$ is the property elicited by the loss $\ell: \R \to \reals^\Y$.
%   \item $d$ is the dimension of the embedding space
%   \item $L:\reals^d \to \reals^\Y_+$ is a loss taking a report $u \in \reals^d$ and mapping the loss over each outcome in $\Y$. \raf{Changed to $\reals^\Y_+$ below.}
%   \item $\Gamma: \simplex \toto \reals^d$ is the set-valued property mapping a probability distribution to a report $u \in \reals^d$.
%   \item $\Gamma_u = \{ p \in \simplex : u \in \Gamma(p) \}$
%   \item $\psi$ is the link function (see below)
%   \item $\varphi:\R \to \reals^d$ is the embedding function
%   \item $\trim(\Gamma)$ and $\strip(\Gamma)$
%   \item $\eliccvx$, $\elicembed$, and $\elicpoly$
%   \item $V$ and $B(P)$ as we get ready for later.
% \end{itemize}

\section{Setting}
\label{sec:setting}

For discrete prediction problems like classification, due to hardness of directly optimizing a given discrete loss, many machine learning algorithms can be thought of as minimizing a surrogate loss function with better optimization qualities, e.g., convexity.
Of course, to show that this surrogate loss successfully addresses the original problem, one needs to establish consistency, which depends crucially on the choice of link function that maps surrogate reports (predictions) to original reports.
We thus begin with a sufficient condition for link functions, after introducing our notation.

\subsection{Notation and Losses}

Let $\Y$ be a finite outcome (label) space, and throughout let $n=|\Y|$.
The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
\jessie{Given labeled data of the form $(x,y)$, we abstract away the data input and consider the conditional probabilities $p(Y|X)$, and this is what we denote as $p_y$.}
\jessiet{Do we want to go into the detail of thinking of $p_y$ as $p(Y|X)$ in finite data}

\raf{Important TODO: we use $\reals^\Y$ sometimes and $\reals^\Y_+$ other times; ideally both $+$, but we need to see what we can prove...  I know this is a key detail for polyhedral losses, to ensure the inf is always attained.}
\jessiet{If the convex loss is bounded from below by $M$, we can say $\reals^\Y_+$ WLOG since $L$ elicits $\Gamma$ implies $(L +c)$ elicits $\Gamma$ for any constant $c$-- in particular, $M$.  We might also assume our discrete loss is nonnegative?}

We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\Delta(\Y)$.
Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$.
(A generic loss be written $L:\R\to\reals^\Y$.)
We write expected loss of report $r$ when $Y \sim p$ as $\inprod{p}{L(r)}$.
The \emph{Bayes risk} of a loss $L:\R\to\reals^\Y$ is the function $\risk{L}:\Delta(\Y)\to\reals$ given by $\risk{L}(p) := \inf_{r\in\R} \inprod{p}{L(r)}$; naturally for discrete losses we will write $\risk{\ell}$.

For example, 0-1 loss is a discrete loss with $\R = \Y = \{1,2,\ldots,n\}$ given by $\ell(r)_y = \Ind[r \neq y]$, and has Bayes risk $\risk{\ell}(p) = \max_{y\in\Y} p_y$.
Two important examples of surrogates for 0-1 loss, with $\R=\reals$, are hinge loss $L(u)_y = \max(0,1-yu)$ and logistic loss $L(u)_y = \log(1+\exp(-yu))$.
\jessiet{Do we want to mention $r \to$ discrete reports and $u \to$ real reports?}

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex\jessiet{and bounded from below?}; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
%
\begin{definition}[Polyhedral loss]
  A loss $L: \reals^d \to \reals^{\Y}_+$ is a \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
\end{definition}
%
For example, the hinge loss is polyhedral, whereas logistic loss is not.

@@

We omit the details connecting this definition to consistency, and instead refer the reader to Ramaswamy et al.~\cite{ramaswamy2018consistent}.
(See the proof of Theorems 8.1-8.3.).
\raf{We could flesh this out if we want.  Might be worth it.  Their entire proof(s) establish $\delta$-separation, and then the line ``The Theorem simply follows from linearity of expectation.''}

Several consistent convex surrogates in the literature can be thought of as ``embeddings'': map the discrete reports to a vector space, and find a convex loss which agrees with the original loss and has the same statistical behavior.
We formalize this notion as follows.
%
\begin{definition}\label{def:loss-embed}
  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
  (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
  \begin{equation}\label{eq:embed-loss}
    r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
  \end{equation}
\end{definition}
%
Note that embeddings do not automatically give rise to separated links; indeed, apart from mapping the embedded reports back from whence they came \raft{I know... just wanted to say that} via $\psi(\varphi(r)) = r$, how to map the remaining values is far from clear.
Constructing separated links from embeddings will therefore be a major focus in Section~\ref{sec:poly-loss-embed}.

\raf{How hinge and abstain fit in}
\jessie{Added the paragraphs below.}
To illustrate the idea of embeddings, we now look in detail at two key examples.
First, consider a binary classification problem on the outcomes $\{-1, +1\}$.
We know that both the hinge loss $L_{hinge}(u,y) := (1 - uy)_+$ and logistic loss $L_{logistic}(u,y) := \ln\left(1 + \exp(-uy)\right)$ are convex surrogates that are minimized in expectation by predicting the mode, as is 0-1 loss $\ell_{mode}(r,y) := \textbf{1}[r\neq y]$.
However, we say that hinge loss embeds the mode, while logistic loss does not.
\jessie{Come back to flesh this out if space?}

In another example, we consider the abstain loss and an embedding given by Ramaswamy et al.~\cite{ramaswamy2018consistent} in Section~\ref{sec:examples}, but note that the link function they provide is not unique.
Essentially, the discrete abstain$(1/2)$ loss is minimized in expectation by predicting the most likely outcome $\argmax_y p_y$, conditioned on $p_y \geq 1/2$.
If the most likely outcome is not likely enough, the loss is minimized by ``abstaining'' from predicting; a situation one can imagine would be useful if a false positive is costly.
\jessie{Are we adding discussion about the choice of link relative to the norm?}

@@

For finite properties and discrete losses, we will use lowercase notation $\gamma$ and $\ell$, respectively, while $\Gamma$ and $L$ will be used for surrogate or general properties.
Often we will work with two properties simultaneously, a finite property $\gamma:\simplex\toto\R$, and its embedded version $\Gamma:\simplex\toto\reals^d$.
In this case, we write the embedded reports as $u\in\reals^d$, reserving $r\in\R$ for the finite property.

\raf{Again, not sure we'll even need the property versions...}
With this terminology in hand, we can restate our definition of embedding.
First, we formalize the notion of embedding properties.
\begin{definition}
  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
\end{definition}
We can now see that a surrogate $L:\reals^d\to\reals^\Y$ embeds $\ell:\R\to\reals^\Y$ if and only if $\prop{L}$ embeds $\prop{\ell}$ via $\varphi$ and for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$.

\subsection{Important Examples}\label{sec:important-examples}
\raf{Probably should move this up to where we introduce embeddings.}

  Ranking and classification problems are well-known to the field of machine learning.
  The most studied classification problem is the elicitation of the mode.
  While the mode over $n$ outcomes is elicitable by 0-1 loss, it is known that eliciting the mode by a convex loss is much more difficult.
  In fact, the best convex surrogate that can be used to elicit the mode ``embeds'' the reports into $\reals^{n-1}$.
  Therefore, we say $\eliccvx($mode$) = n-1$.

  A property of interest similar to the mode is the $\abstain{\alpha}$ property.
  In this property in which one reports the most likely outcome if the probability of such an outcome is greater than $1-\alpha$, and otherwise ``abstains'' from reporting.
  That is, $\gamma(p) = \argmax_{r \in \R}p_r$ if $\max_{r \in \R} p_r \geq 1-\alpha$ and is ``abstain'' otherwise.
  The finite loss eliciting $\abstain{\alpha}$ can be written
  $\ell(r,y) = 0$ if $r=y$, $\alpha$ if $r=\text{abstain}$, and $1$ otherwise.
\cite{ramaswamy2018consistent} show that $\elicpoly(\abstain{1/2}) \leq \ceil{\log_2 n}$, although it is not known if this bound is tight.

@@

In this section, we establish a tight relationship between the technique of embedding and the use of polyhedral (piecewise-linear convex) surrogate losses.
Note that we have not yet shown consistency of such surrogates; this is the topic of the following section.

To begin, we observe that our embedding condition in Definition~\ref{def:loss-embed} can be very succinctly rewritten: it is equivalent to matching Bayes risks.
This useful result will drive many of our findings in this section.

\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
  \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
  \jessie{Stated in COLT Lemma 11 and Prop 12 (Lemma~\ref{lem:finite-full-dim} and Prop~\ref{prop:embed-trim} here), but I don't see us prove this in the original paper.}

  \jessie{The forward implication is a corollary of COLT Lemma 11}

  %Jessie's first attempt at a proof
  First, suppose $L$ embeds $\ell$, and fix $p \in \simplex$.
  We want to show for all $p \in \simplex$ that $\inf_{u\in\reals^d} L(u,p) = \min_{r \in \R} \ell(r, p)$.
  Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
  Then
  \begin{align*}
  \inf_u L(u,p) = \min_{r \in \R} L(\varphi(r), p) = \min_{r \in \R} \ell(r, p)
  \end{align*}
   first by the case assumption and then by the definition of embedding.
  Now in the second case, if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
  Therefore, $r \in \argmin_r' \ell(r', p) \implies \varphi(r) \not \in \argmin_u L(u,p)$ which contradicts the assertion that $L$ embeds $\ell$.

  \jessie{Not sure on this one, just FYI.  I think it's a corollary of COLT Prop 12, now Prop~\ref{prop:embed-trim}.}
  Now, to see that $\risk{\ell} = \risk{L} \implies L$ embeds $\ell$, consider $F$ to be the set of facets of the surface of $\risk{L}$.
  For each facet $f \in \F$, we know by nonredundancy that there is some $p \in \inter{f}$ so that $\risk{L}$ is differentiable at $p$.
  Moreover, by Frongillo and Kash~\cite[Theorem 2?]{frongillo2014general} \jessie{Check ref} we know that both $\ell$ and $L$ have a unique minimizer at $p$, and since the subgradients of the risks are the same (by their equality), we know the minimizers of the losses are also the same, up to relabeling the reports via a bijection.
  Therefore, we can see that $L$ embeds $\ell$, as $L(\varphi(r),y) = \ell(r,y)$ for all $r\in\R$ and $y \in \Y$.
  \jessie{Incomplete...?}

%  Now let us show that $\risk{L} = \risk{\ell} \implies L$ embeds $\ell$.
%  Let $F$ be the set of facets in $\risk{\ell}$.
%  For each $f \in F$, there is some $p \in \inter{f}$ so that $\risk{L}(p) = \risk{\ell}(p)$ is differentiable, and so the loss $L$ must then be uniquely defined.
%  \jessie{This is my interpretation of your note, but I don't see how this proves the existence of an embedding.  My inclination is to show there's the ``stripped'' loss that we embed ($\varphi(u) = u$) and for any bijection $\phi$, we can see that $\ell$ can be modified to $\ell^\phi$ so that $\risk{\ell} = \risk{\ell^\phi}$, and $L$ also embeds $\ell^\phi$ with $\varphi(r) = \phi(r)$.  Does that make sense?}

\end{proof}

@@

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  \jessie{My attempt below}
  For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
  By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral. \jessie{Need to prove? Stated as fact in proof of COLT Prop 12...}
  Therefore, $\risk{L}$ is polyhedral.

@@

\begin{theorem}\label{thm:poly-embeds-discrete}
  Every polyhedral loss $L$ embeds a discrete loss.
\end{theorem}
\begin{proof}
  We merely show $L$ polyhedral $\implies$ $\risk{L}$ polyhedral, and apply Proposition~\ref{prop:embed-risk-poly}.
  \raf{Not sure how trivial this is, but it's definitely true.  I suspect it has a very short proof.}
  \jessie{$L(u,p)$ polyhedral in $\reals^d$ implies $L^*(0,p) = -\risk{L}(p)$ polyhedral in $\simplex$ implies $\risk{L}$ polyhedral.
  Now we can apply Proposition~\ref{prop:embed-risk-poly} to observe the result.}

  \jessie{Can also show that $L$ embeds $L|_\R$ like the original paper and use COLT Lemma 11/Lemma~\ref{lem:finite-full-dim}.}
\end{proof}

We now turn to the reverse direction: is every discrete loss embedded by some polyhedral loss?
Using a construction via convex conjugate duality, which has appeared several times in the literature\raft{CITE: DKR, frongillo-kash (WINE 2014), probably one of Bob's papers?, others?}, we see that the answer is yes, although the number of dimensions $d$ required could be as large as $n-1$.
\raft{Should revisit this statement at the end; I have a feeling we'll want to kill ``$n$'' throughout the paper since we focus so much less on it, and the reader won't remember what $n$ is.}

\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
  Every discrete loss $\ell$ is embedded by a polyhedral loss.
\end{theorem}
\begin{proof}
  \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
  \jessie{Might try tonight without properties?}
\end{proof}

We have seen a tight connection between embeddings and polyhedral losses\raf{... what else can we say here?  Why is this cool?}

To conclude, we briefly point out the interesting implications of these results on the structure of embedded \emph{properties} themselves.
In particular, the following corollary states an equivalence between finite elicitable properties, embeddable properties, and properties embedded by polyhedral losses.

\begin{corollary}\label{cor:finite-elicit-embed}
  Let $\gamma$ be a finite property.
  The following are equivalent.
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\gamma$ is elicitable.
  \item $\gamma$ is embeddable.
  \item $\gamma$ is embeddable via a polyhedral loss.
  \end{enumerate}
\end{corollary}
\begin{proof}
  We trivially have $3\Rightarrow 2$.
  The direction $1\Rightarrow 3$ follows from Theorem~\ref{thm:discrete-loss-poly-embeddable}, by taking any discrete loss which elicits $\gamma$.
  Finally, to see $2\Rightarrow 1$,
  \raf{This follows from Proposition~\ref{prop:embed-trim}, but we're stating this as a corollary... let's see if it follows more directly from the above.  If it doesn't (one complication: there is no discrete loss starting from $2$ or $3$!) we can rephrase it as a theorem / proposition.}
\end{proof}

@@

When working with convex losses which are not strictly convex, one quickly encounters redundant properties: if $\inprod{p}{L(\cdot)}$ is minimized by a point where $p\cdot L$ is flat, then there will be an uncountable set of reports which also minimize the loss.
As results in property elicitation typically assume non-redundant properties (e.g.~\cite{frongillo2014general,frongillo2015elicitation}) it is useful to consider a transformation which removes redundant level sets.
We capture this transformation as the trim operator presented below.

@@

Take note that the unlabeled property $\trim(\Gamma)$ is non-redundant, meaning that for any $\theta \in \trim(\Gamma)$, there is no level set $\theta' \in \trim(\Gamma)$ such that $\theta \subset \theta'$.

>>>>

\documentclass[12pt]{article}
\PassOptionsToPackage{numbers, compress, sort}{natbib}
\usepackage{../neurips-19/neurips_2019}

@@

@@

%
\begin{definition}[Polyhedral loss]
  A loss $L: \reals^d \to \reals^{\Y}_+$ is a \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
\end{definition}

@@

\begin{definition}\label{def:loss-embed}
  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ if there exists some injective embedding $\varphi:\R\to\reals^d$ such that
  (i) for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
  \begin{equation}\label{eq:embed-loss}
    r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
  \end{equation}
\end{definition}

@@

\begin{definition}
  A property $\Gamma : \simplex \toto \reals^d$ \emph{embeds} a property $\gamma : \simplex \toto \R$ if there exists some injective embdedding $\varphi:\R\to\reals^d$ such that for all $p\in\simplex,r\in\R$ we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
  Similarly, we say a loss $L:\reals^d\to\reals^\Y$ embeds $\gamma$ if $\prop{L}$ embeds $\gamma$.
\end{definition}
We can now see that a surrogate $L:\reals^d\to\reals^\Y$ embeds $\ell:\R\to\reals^\Y$ if and only if $\prop{L}$ embeds $\prop{\ell}$ via $\varphi$ and for all $r\in\R$ we have $L(\varphi(r)) = \ell(r)$.

@@

\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}[Non-property version]
  \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
  %Jessie's first attempt at a proof
  First, suppose $L$ embeds $\ell$, and fix $p \in \simplex$.
  We want to show for all $p \in \simplex$ that $\inf_{u\in\reals^d} L(u,p) = \min_{r \in \R} \ell(r, p)$.
  Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
  Then
  \begin{align*}
  \inf_u L(u,p) = \min_{r \in \R} L(\varphi(r), p) = \min_{r \in \R} \ell(r, p)
  \end{align*}
   first by the case assumption and then by the definition of embedding.
  Now in the second case, if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
  Therefore, $r \in \argmin_r' \ell(r', p) \implies \varphi(r) \not \in \argmin_u L(u,p)$ which contradicts the assertion that $L$ embeds $\ell$.

  \jessie{Not sure on this one, just FYI.  I think it's a corollary of COLT Prop 12, now Prop~\ref{prop:embed-trim}.}
  Now, to see that $\risk{\ell} = \risk{L} \implies L$ embeds $\ell$, consider $F$ to be the set of facets of the surface of $\risk{L}$.
  For each facet $f \in \F$, we know by nonredundancy that there is some $p \in \inter{f}$ so that $\risk{L}$ is differentiable at $p$.
  Moreover, by Frongillo and Kash~\cite[Theorem 2?]{frongillo2014general} \jessie{Check ref} we know that both $\ell$ and $L$ have a unique minimizer at $p$, and since the subgradients of the risks are the same (by their equality), we know the minimizers of the losses are also the same, up to relabeling the reports via a bijection.
  Therefore, we can see that $L$ embeds $\ell$, as $L(\varphi(r),y) = \ell(r,y)$ for all $r\in\R$ and $y \in \Y$.
  \jessie{Incomplete...?}
\end{proof}
\hline
\begin{proof}[Property version]
  \jessie{TODO}
  \jessie{Stated in COLT Lemma 11 and Prop 12 (Lemma~\ref{lem:finite-full-dim} and Prop~\ref{prop:embed-trim} here), but I don't see us prove this in the original paper.}

  \jessie{The forward implication is a corollary of COLT Lemma 11}
\end{proof}

@@

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}[Property version]
	\jessie{TODO}
\end{proof}
\hline
\begin{proof}[Non-property version]
  For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
  By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral.
  Therefore, $\risk{L}$ is polyhedral.

@@

\begin{theorem}\label{thm:poly-embeds-discrete}
  Every polyhedral loss $L$ embeds a discrete loss.
\end{theorem}
\begin{proof}[Non-property version]
  We merely show $L$ polyhedral $\implies$ $\risk{L}$ polyhedral, and apply Proposition~\ref{prop:embed-risk-poly}.
  \raf{Not sure how trivial this is, but it's definitely true.  I suspect it has a very short proof.}
  \jessie{$L(u,p)$ polyhedral in $\reals^d$ implies $L^*(0,p) = -\risk{L}(p)$ polyhedral in $\simplex$ implies $\risk{L}$ polyhedral.
  Now we can apply Proposition~\ref{prop:embed-risk-poly} to observe the result.}

  \jessie{Can also show that $L$ embeds $L|_\R$ like the original paper and use COLT Lemma 11/Lemma~\ref{lem:finite-full-dim}.}
\end{proof}
\hline
\begin{proof}[Property version]
  To see this, we construct one such discrete loss, namely $L|_\R$, where $\R := \{u_f\}_{f \in F}$ is the set of reports that are uniquely optimal on the interior of each full-dimensional level set.

  Given the loss $L$, consider $\Gamma := \prop{L}$.
  We know that $\Gamma$ embeds $\gamma := \Gamma \cap \R$ via the identity embedding. \jessie{Cite}
  Moreover, $\ell := L|_\R$ elicits $\gamma$, and thus we can conclude that $L$ embeds the discrete loss $L|_\R$.
\end{proof}

\begin{theorem}\label{thm:discrete-loss-poly-embeddable}
  Every discrete loss $\ell$ is embedded by a polyhedral loss.
\end{theorem}
\begin{proof}
  \raf{Already have the proof from Theorem~\ref{thm:general-duality-embedding}.  Should cite DKR and others...}
  \jessie{Might try tonight without properties?}
\end{proof}
\hline
\begin{proof}[Property version]
	\jessie{TODO}
\end{proof}

\begin{corollary}\label{cor:finite-elicit-embed}
  Let $\gamma$ be a finite property.
  The following are equivalent.
  \begin{enumerate}\setlength{\itemsep}{0pt}
  \item $\gamma$ is elicitable.
  \item $\gamma$ is embeddable.
  \item $\gamma$ is embeddable via a polyhedral loss.
  \end{enumerate}
\end{corollary}
\begin{proof}[Non-property version]
  We trivially have $3\Rightarrow 2$.
  The direction $1\Rightarrow 3$ follows from Theorem~\ref{thm:discrete-loss-poly-embeddable}, by taking any discrete loss which elicits $\gamma$.
  Finally, to see $2\Rightarrow 1$,
  \raf{This follows from Proposition~\ref{prop:embed-trim}, but we're stating this as a corollary... let's see if it follows more directly from the above.  If it doesn't (one complication: there is no discrete loss starting from $2$ or $3$!) we can rephrase it as a theorem / proposition.}
\end{proof}
\begin{proof}[Property version]
	\jessie{TODO}
\end{proof}

@@

@@
